\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-09 paper/draft.tex
Update abstract
Conclusion

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
This paper presents \sys, a system for parallelizing POSIX shell scripts through a combination of program transformations and runtime primitives.
% a source-to-source shell compiler and associated runtime library
Given a script, \sys converts it to a dataflow graph, performs a series of transformations that expose parallelism while preserving its sequential semantics, and then converts the dataflow graph back into a script that uses POSIX constructs to explicitly guide parallelism.
A lightweight annotation language allows command developers to express key parallelizability properties about their commands.
An accompanying parallelizability study of POSIX and GNU commands---two large and commonly used groups---guides the annotation language and optimized aggregator library that \sys uses.
% \kk{eurosys: Can we extend this to say that PaSh automatically uses constructs from this library? Otherwise it sounds like the user has to use it to make their scripts parallel.}
Finally, \sys's \unix-aware runtime primitives address several practical issues related to performance and correctness.
\sys's extensive evaluation over 44 unmodified \unix scripts shows significant speedups ($0.89$--$61.1\times$, avg: $6.7\times$) stemming from the combination of its program transformations and runtime primitives.
% The vast majority (39/44) of scripts---all unmodified---see significant speedups (average over all is $6.7\times$, up to $61\times$).
\end{abstract}

@@

This paper presented \sys, a system allowing shell users to parallelize shell programs mostly automatically.
% a source-to-source shell compiler and associated runtime library
\sys consists of (i) a source-to-source compiler, which transforms scripts to DFGs, parallelizes them, and transforms them back to scripts; and (ii) a runtime component that addresses several practical challenges related to performance and correctness.
Our evaluation on a wide variety of \emph{unmodified} scripts shows that \sys achieves significant speedups due to parallelism (total avg: $6.7\times$) in the vast majority of them (39/44), including scripts that perform mundane tasks such as downloading, extracting, and cleaning data, which are usually not the focus of parallelization systems.
\sys is open source and available for download online~[Blind].

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
This paper presents \sys, a system for parallelizing POSIX shell scripts through a combination of program transformations and runtime primitives.
Given a script, \sys converts it to a dataflow graph, performs a series of transformations that expose parallelism while preserving its sequential semantics, and then converts the dataflow graph back into a script that uses POSIX constructs to explicitly guide parallelism.
A lightweight annotation language allows command developers to express key parallelizability properties about their commands.
An accompanying parallelizability study of POSIX and GNU commands---two large and commonly used groups---guides the annotation language and optimized aggregator library that \sys uses.
Finally, \sys's \unix-aware runtime primitives address several practical issues related to performance and correctness.
\sys's extensive evaluation over 44 unmodified \unix scripts shows significant speedups ($0.89$--$61.1\times$, avg: $6.7\times$) stemming from the combination of its program transformations and runtime primitives.
\end{abstract}

% a source-to-source shell compiler and associated runtime library
% \kk{eurosys: Can we extend this to say that PaSh automatically uses constructs from this library? Otherwise it sounds like the user has to use it to make their scripts parallel.}
% The vast majority (39/44) of scripts---all unmodified---see significant speedups (average over all is $6.7\times$, up to $61\times$).

@@

Shell programs are ubiquitous, utilize programs from a plethora of programming languages, and spend a significant fraction of their time interacting with the broader environment to download, extract, and process data---falling outside the focus of conventional parallelization systems.
This paper presents \sys, a system that allows shell users to parallelize shell programs mostly automatically.
\sys can be viewed as (i) a source-to-source compiler that transforms scripts to DFGs, parallelizes them, and transforms them back to scripts; coupled with (ii) a  runtime component that addresses several practical challenges related to performance and correctness.
\sys's extensive evaluation over 44 unmodified Unix scripts demonstrates non-trivial speedups (0.89--61.1$\times$, avg: 6.7$\times$).
\sys is open source and available for download~[Blind].
